Analysis on The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying

### 2023-02-21 Outputs/Paper/paper.qmd
added low asian datasets
Slightly changed download data script. Added data cleaning with respect to bottom 10 asian population states. Added to the paper in the top 10 vs bot 10 comparison section, and csv reading

sum_bully_data <- read.csv(here::here("Outputs/data/sum_bully_data.csv"))
sum_cybully_data <- read.csv(here::here("Outputs/data/sum_cybully_data.csv"))
sum_schbully_data <- read.csv(here::here("Outputs/data/sum_schbully_data.csv"))

@@

@@

To analysis these data, R programing language (@citeR), tidyverse (@citeTidyverse), and dplyr (@citedplyr) are used. ggplot2 (@citeggplot2) has been used in order to produce graphic reports. The use of knitr (@citeknitr) helped us to generate tables. Lubridate (@citelubridate) are used to reformat dates.

@@

>>>>

#Reading data for top 10 asian population
sum_bully_data <- read.csv(here::here("Outputs/data/sum_bully_data.csv"))
sum_cybully_data <- read.csv(here::here("Outputs/data/sum_cybully_data.csv"))
sum_schbully_data <- read.csv(here::here("Outputs/data/sum_schbully_data.csv"))

@@

#Reading data for bot 10 asian population
sum_bully_lowasp_data <- read.csv(here::here("Outputs/data/sum_bully_lowasp_data.csv"))
sum_cybully_lowasp_data <- read.csv(here::here("Outputs/data/sum_cybully_lowasp_data.csv"))
sum_schbully_lowasp_data <- read.csv(here::here("Outputs/data/sum_schbully_lowasp_data.csv"))

cleaned_bully_lowasp_data <- read.csv(here::here("Outputs/data/cleaned_schbully_lowasp_data.csv"))
cleaned_cybully_lowasp_data <- read.csv(here::here("Outputs/data/cleaned_schbully_lowasp_data.csv"))
cleaned_schbully_lowasp_data <- read.csv(here::here("Outputs/data/cleaned_schbully_lowasp_data.csv"))

@@

To analysis these data, R programming language (@citeR), tidyverse (@citeTidyverse), and dplyr (@citedplyr) are used. ggplot2 (@citeggplot2) has been used in order to produce graphic reports. The use of knitr (@citeknitr) helped us to generate tables. Lubridate (@citelubridate) are used to reformat dates.

@@

```{r}
#| label: lowaspgraph
#| fig-cap: Bullying searches in the lowest Asian population states.
#| echo: false
#| warning: false

sum_bully_lowasp_data |> ggplot(aes(x = date, y = sum)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 8)) +
  labs(
    title = "All 'Bullying' Searches in Low Asian Population States",
    x = "Date",
    y = "Search Frequency",
    fill = "State Name"
  )

sum_cybully_lowasp_data |> ggplot(aes(x = date, y = sum)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 8)) +
  labs(
    title = "'Cyberbullying' Searches in Low Asian Population States",
    x = "Date",
    y = "Search Frequency",
    fill = "State Name"
  )

sum_schbully_lowasp_data |> ggplot(aes(x = date, y = sum)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 8)) +
  labs(
    title = "'School Bullying' Searches in Low Asian Population States",
    x = "Date",
    y = "Search Frequency",
    fill = "State Name"
  )
```

Figure 6 shows the bullying searches in states with the bottom 10 Asian population. In all three metrics, there is a decrease in bullying searches in comparison to bullying searches in the top 10 states. The data shows that having a high population of Asian people did have an effect on school bullying searches during the pandemic. The higher the Asian population, the more bullying searches there were.

However, one weakness of this comparison is that there is sampling bias with this set. The total population numbers for the bottom 10 Asian population states are dwarfed by the total population numbers of the top 10 Asian population states. So naturally, there would be less bullying searches in a state like Montana, which has around 2.7% of California's total population. This is where our approach of using raw search data reaches it's limit, as we cannot draw an accurate comparison of search ratios due to the massive difference in total population numbers.
